---
title: "First MarkDown"
author: "Hossein Noorazar"
date: "8/5/2018"
output: html_document
  # beamer_presentation: default
  # ioslides_presentation: default

# to make it reactive uncomment below:
runtime: shiny

---

 ```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
 ```

```{r echo = FALSE}
selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20)
  
sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
```

### ...that build a histogram.

```{r echo = FALSE}
renderPlot({
  hist(faithful$eruptions, probability = TRUE, 
       breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", 
       main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```



## New slide
some content

*** 
Slide without a title
What goes on here. so the '***' starts a new slide without
any title.

## Title
### Top level subheading
#### A second level subheading
what goes here is usual text

- *italicized text comes with one asteric on each end of the text, just like youtube bold-maker.*
- **Bold comes with two asetrix at each end.**
- Code comes with a (\`) at each end: 

   <center> `for i in len(range(x))` </center>

## R-code slide having R code ran in it.

```{R, comment="", echo=TRUE}
head(mtcars)
```

## Plot slide

```{r, echo=FALSE, fig.align='center', fig.cap="First Figure"}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```






## R Markdown

This is an R Markdown presentation. Markdown is a 
simple formatting syntax for authoring HTML, PDF, 
and MS Word documents. For more details on using 
R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document 
will be generated that includes both content 
as well as the output of any embedded R 
code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

